Supplementary Materials for: ``Well-Designed Environmental Markets Enable Large-Scale Marine Conservation''

### 2019-10-25 docs/Markets_Conservation_revised_Oct24.tex
Updated docs folder

A large-scale MPA was recently implemented in PNA waters, providing the ideal empirical setting to test our predictions. In January 2015, Kiribati closed 11.5\% of its EEZ to implement the Phoenix Island Protected Area (PIPA), effectively displacing all fishing effort within its boundaries\cite{mccauley_2016,mcdermott_2018}. By protecting important tuna spawning habitat, PIPA may provide important recruitment and biomass benefits to adjacent waters \cite{hernndez_2019}. We combine vessel-tracking data \cite{kroodsma_2018} and country-level license revenue data reported by the Pacific Islands Forum Fisheries Agency (FFA) \cite{ffa_2017} to quantify the displacement of vessel-days and the likely costs of conservation. Of the 318 tuna purse seine vessels that fished in PNA waters between 2012 and 2018, 64 ``displaced'' vessels fished within PIPA at least once prior to its implementation and 254 ``non-displaced vessels'' never fished in PIPA waters but fished within the PNA waters. We use the tracking data to calculate vessel-days in the same way that the PNA does (see Methods for details) and the redistribution of fishing events before and after the implementation of PIPA.

@@

The decrease of vessel-days in Kiribati could be alternatively (or jointly) explained by changes in oceanographic conditions that drive distribution of target species and fishing vessels. For example, as El Ni\~no events develop, tuna species are known to shift longitudinally across PNA waters, causing vessels to redistribute \cite{aqorau_2018,hanich2018unraveling}. However, the total decrease that we observe for Kiribati in Fig. \ref{fig:empirical} is driven by the relocation of vessels that once fished within PIPA, not by the entire fleet. One could argue that differences in vessel characteristics between displaced and non-displaced vessels may influence their ability to redistribute or take advantage of different oceanographic conditions in Kiribati. For example, on average, displaced vessels have smaller crew sizes, more engine power, and are larger than non-displaced vessels (Table S2, Fig. S5). However, displaced vessels gradually reduce their time spent in PNA waters.

As predicted by our model, the implementation of PIPA resulted in a decrease in fishing effort within Kiribati's water without large revenue losses. Kiribati's reported revenue increased from US\$127.3 million in 2014 to US\$148.8 million in 2015, before decreasing to US\$118.3 million in 2016 (Fig. \ref{fig:empirical}C). The increase and subsequent decrease in revenues matches the vessel-day patterns observed for Kiribati from 2014 to 2016 (Fig. \ref{fig:empirical}D). But, critically, the drop in revenue in 2016 (20\%) is smaller than the drop in VDS effort (35\%). This supports a key prediction of our model: with trading, the relative revenue drop will always be smaller than the relative effort drop but, without trading, the opposite relationship would hold (Fig. S4). At the PNA level, total revenues showed a net increase of \$64.7 and \$28 million USD for 2015 and 2016 respectively (Fig. S8), despite the PIPA closure.

@@

%%%% PLEASE TAKE A LOOK AT THE SECOND SENTENCE OF THIS PARAGRAPH %%%%
While trading would allow Palau, Kiribati, and other PNA members to reduce revenue losses from large-scale conservation, our model indicates that moving from a 40\% biomass-based allocation rule to a 100\% biomass-based rule would ensure long-term financial security in the presence of large-scale MPAs, and further incentivize conservation within the PNA. However, it is worth mentioning that we did not empirically test this prediction, as this would imply modifying the allocation rule in the real world. The Parties to the Nauru Agreement have shown that rights-based management of transboundary resources can result in large management and economic benefits \cite{havice_2013,aqorau_2018}. By facilitating trade and allocating rights based on biomass, they may become pioneers in effective large-scale marine conservation in a market-based setting.

There are, however, a series of important considerations to take into account. First, in our study only one of the countries considers the implementation of a protected area. However, an interesting extension would be that of cooperative conservation. In that setting, a group of countries could coordinate on an optimized, large-scale strategic closure -perhaps using vessel-day trading as a means of compensation- in a manner similar to the model above. Future research could explore the role of heterogeneous costs and benefits between countries, and the way in which these can shape conservation outcomes in a market-based setting. A second consideration is that of the role that the high seas play: environmental markets require secure property rights, which are lacking in the high seas \cite{crespo_2019}. Any spillover into the high seas could potentially be eroded by the prevailing open access conditions. Therefore, a conservation-minded nation has no mechanism to capture the benefits provided to the high seas, highligting the importance of empowering high seas governance and transboundary cooperation \cite{aqorau_2018,crespo_2019}. Finally, our work focuses on fisheries and large-scale conservation, but the framework could potentially be expanded and applied to other systems and natural resources. For example, similar mechanisms could be implemented in markets for tradable water rights \cite{rosegrant_1994} or game hunting \cite{hutton_2003} where secure property rights and the presence of a market may incentivise users to conserve the resource in question.

The use of environmental markets for conservation is a common but contentious approach among conservation scientists and resource managers \cite{sandbrook_2019}. One of the driving concerns is that markets may create incentives that lead to undesirable outcomes, thus emphasizing the need for careful design. We show that individual countries have little incentive to undertake large-scale marine conservation, but that this incentive can be reversed if those countries are in an appropriately-designed market-based setting. For the market to create these incentives, certain design features are paramount. In the case of fishing rights and MPAs, cross-country transferable fishing rights and a biomass-based allocation rule are two necessary conditions to achieve the conservation incentive. International goals over the next decade have set ambitious targets for terrestrial and marine conservation, which will provide benefits ranging from preserving biodiversity to enhancing human well-being \cite{oleary_2016,dinerstein_2019,roberts_2017,ban_2019}. Our work shows how well-designed environmental markets can provide the right incentives for effective large-scale marine conservation.

@@

Country 1 considers a spatial closure by implementing a reserve as a fraction $R$ of the total country ($R \in[0,1)$). Fish move within a country based on $\theta$, where $\theta = 0$ implies no movement within the country, and $\theta = 1$ implies that fish move so much that they can be caught from anywhere within the country (see the \emph{Notes on within-country fish movement} section below). In this country, revenues are given by $pqE_1X_1(\theta + (1 - \theta)(1 - R))$. The parameterization of movement and reserve size imply that profit from fishing Country 1 is given by:

@@

\noindent with $\Omega_1 = (\theta + (1 - \theta)(1 - R))$ being a parameterization that combines reserve size as a proportion of country ($R =  [0, 1)$) and within-country fish movement ($\theta$). Under this parameterization, $\Omega_{i \neq 1} = 1$ since only Country 1 implements a reserve.

@@

\noindent The above equations imply that the marginal profit from the last unit of effort in a country are given by:

@@

In practice, the effort levels in each country are allocated by management (so $E_{1},\ E_{2},...,E_{9}$ are given) and the effort level on the high seas ($E_{10}$) is a result of open access dynamics. Therefore, we assume that effort continues to enter Country 10 until the profit from the last unit of effort is exactly zero, indicating that $E_{10}$ is the value for which $\pi_{10}(E_{10})  = 0$. Setting Equation \ref{eqn:marginal_profit} for $i = 10$ equal to zero and removing $\Omega_{10} = 1$ for simplicity, we can solve for $E_{10}$:

@@

\begin{equation}
X_{t+1} = e_t \times  e^{r \left(1 - \frac{e_t}{K} \right)}
\label{eqn:grow}
\end{equation}

\noindent where $r$ and $K$ are species-specific intrinsic growth rate and carrying capacity. After the stock grows, a constant and country-specific fraction $f_i$ of the total stock redistributes to country $i$, so:

@@

In our model parameterization, the proportion of biomass ``available'' for harvest is given by  $\Omega_1 = (\theta + (1 - \theta)(1 - R))$. This implies that for a given country with stock size $X_i$, the total biomass available for harvest will be given by $\Omega X_i$. Consider the case of a sesile fish with $\theta = 0$. If the country were to close 50\% of its waters to fishing ($R = 0.5$), only 50\% of the stock would be available for harvest (\emph{i.e.} $0 + (1 - 0) * (1 - 0.5) = 0.5$). Now, consider the same closure is applied with a stock with high mobility, so $\theta = 0.9$. In this case, despite the closure, fish constantly swim between the reserve and fishing grounds making 95\% of biomass available for harvest (\emph{i.e.} $0.9 + (1 - 0.9) * (1 - 0.5) = 0.95$). As derived in the bioeconomic model above, a vessel's willingness to pay to fish in a given patch will be determined by the amount of biomass available for harvest. Within-patch stock movement therefore plays an important role in determinig a vessel's willingness to pay in the remaining open waters: a vessel will be willing to pay more to fish in waters where 95\% of biomass is available for harvest, than when only 50\% of biomass is available for harvest.

@@

We run simulations under two market designs and test the model across a range of reserve sizes and within-country movement parameters.The first scenario does not allow trading. In this case, total allowable effort ($\bar{E}$) and biomass $B_{now}$ are known and equally distributed among Countries 1-9. For Country 10, we solve for Eq \ref{eqn:effort_hs} until biomass converges to match $B_{now}$. We then proceed to ``close'' a portion of Country 1, and calculate the vessel-day price in Country 1 given that only $X_i\Omega_i$ biomass is available for harvest. We compare vessel-day revenues of each scenario to a case with no reserve ($R = 0$). This produces a measure of the cost of implementing a spatial closure of size $R$ in Country 1.

The second scenario allows trading. We start again by solving for the high seas to obtain total effort. Since a closure is not in effect and VDS-managed effort is equally distributed across the 9 countries, this equilibrium is the same as the first step above. We then implement a spatial closure in Country 1. This essentially lowers the price fishers would be willing to pay to fish in a country with only biomass $X_i\Omega_i$, lowering demand for vessel-days in Country 1. Countries 2 - 9 have a higher demand for vessel days, and therefore a portion of vessel-days from Country 1 are sold to Countries 2 - 9. This increases effort in these countries, which reduces escapement and therefore biomass. This reduction in biomass in turn will modify the marginal profit and willingness to pay to fish in each country. We therefore iterate this process until biomass stabilizes, finding the system's equilibrium. Like before, we calculate vessel-day revenues to each country and compare them to a case with no reserve in Country 1.

Annual vessel-days are often allocated based on a combination of historical within-country effort and biomass. In the PNA, 60\% of the allocation is calculated based on EEZ effort over the last seven years and 40\% is calculated based on the 10-year average of each country’s share of estimated biomass (of skipjack and yellowfin tuna) within its EEZ (This is explained in more detail in Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}). Trading vessel-days to other countries would imply that historical within-country effort declines through time. The allocated days to a country with a full spatial closure would eventually be reduced to just the 40\% based on biomass.

In the trading scenario above, effort from Country 1 (with the reserve) is traded to other countries. This means that its allocation will decrease as purse seine effort in its EEZ is reduced. To analyze the consequences of different allocation rules when trading is allowed, we simulate a fishery 50 years into the future, and annually re-allocate vessel-days based on a 7-year running mean of country-level effort and biomass. At the end of every time period (a year), vessel-days are re-allocated to each country based on the following rule:

@@

We can then compare the footprint of displaced and non-displaced vessels before and after the implementation of PIPA to better understand the effort redistribution. Non-displaced vessels serve as a plausible control group that was not subject to a spatial closure but might have redistributed in response to changing environmental conditions, such as El Ni\~no \cite{hanich2018unraveling,aqorau_2018}.

@@

Juan Carlos Villaseñor-Derbez was supported by UCMexus-CONACyT (CVU: 669403) and the Latin American Fisheries Fellowship Program. John Lynham was supported by the Conservation Strategy Fund, with a grant from the Pew Charitable Trusts and Pew Bertarelli Ocean Legacy. John Lynham and Christopher Costello wish to acknowledge The Nature Conservancy.

@@

% Costs of different allocation rules
\begin{figure}[htbp]
\centering
\includegraphics{img/allocation_cost_plot.pdf}
\caption{\label{fig:allocation_cost_plot}Costs of a spatial closure for Country 1 under different allocation rules. Each line represents the revenue losses for a combination of allocation rules ($\alpha$; line type) and movement ($\theta$; color) for different reserve sizes ($R$; horizontal axis). A value of $\alpha = 1$ implies that allocations are based entirely on historical effort, while a value of $\alpha = 0$ implies a 100\% biomass-based allocation rule. A value of $\theta = 0$ represents a stock that doesn't move, and $\theta = 1$ depics a stock that continuously moves between the reserve and the fishing zone. The proportion of the Exclusive Economic Zone closd to fishing is given by $R$. An effort-based allocation and low within-country movement values result in the highest costs. Cost can be minimized for all movement values if allocation is based on biomass within each country’s waters.}
\end{figure}

>>>>

A large-scale MPA was recently implemented in PNA waters, providing the ideal empirical setting to test our predictions. In January 2015, Kiribati closed 11.5\% of its EEZ to implement the Phoenix Island Protected Area (PIPA), effectively displacing all fishing effort within its boundaries\cite{mccauley_2016,mcdermott_2018}. By protecting important tuna spawning habitat, PIPA may provide important recruitment and biomass benefits to adjacent waters \cite{hernndez_2019}. We combine vessel-tracking data \cite{kroodsma_2018} and country-level license revenue data reported by the Pacific Islands Forum Fisheries Agency (FFA) \cite{ffa_2017} to quantify the displacement of vessel-days and the likely costs of conservation. Of the 318 tuna purse seine vessels that fished in PNA waters between 2012 and 2018, 64 ``displaced'' vessels fished within PIPA at least once prior to its implementation and 254 ``non-displaced vessels'' never fished in PIPA waters but fished within the PNA waters. We use the vessel-tracking data to calculate vessel-days in the same way that the PNA does (see Methods for details) and the redistribution of fishing events before and after the implementation of PIPA.

@@

The decrease of vessel-days in Kiribati could be alternatively (or jointly) explained by changes in oceanographic conditions that drive the distribution of target species and fishing vessels. For example, as El Ni\~no events develop, tuna species are known to shift longitudinally across PNA waters, causing vessels to redistribute \cite{aqorau_2018,hanich2018unraveling}. However, the aggregate decrease that we observe for Kiribati in Fig. \ref{fig:empirical} is driven by the relocation of vessels that historically fished within PIPA, not by the entire fleet. Oceanographic conditions should be influencing the entire fleet whereas the closure of PIPA should have a stronger impact on vessels that used to fish there. Thus, the large drop in effort within Kiribati for the displaced vessels (relative to the non-displaced vessels) is consistent with the argument that PIPA displaced these vessels to waters outside of Kiribati. One could argue that differences in vessel characteristics between displaced and non-displaced vessels may influence their ability to redistribute or take advantage of different oceanographic conditions in Kiribati. It should be noted that, on average, displaced vessels have smaller crew sizes, more engine power, and are larger than non-displaced vessels (Table S2, Fig. S5). Another alternative explanation is a change in international relations between Kiribati (or other PNA countries) and the flag country of a particular vessel. Ruling out alternative explanations for observed effects is an important component of careful empirical evaluation of MPAs \cite{ferraro2018causal}: as such, our results should not be interpreted as the direct causal impacts of PIPA but are better viewed as patterns that are consistent with the predictions of our theoretical model.

As predicted by our model, the implementation of PIPA resulted in a decrease in fishing effort within Kiribati's water without large revenue losses. Kiribati's reported revenue increased from US\$127.3 million in 2014 to US\$148.8 million in 2015, before decreasing to US\$118.3 million in 2016 (Fig. \ref{fig:empirical}C). The increase and subsequent decrease in revenues matches the vessel-day patterns observed for Kiribati from 2014 to 2016 (Fig. \ref{fig:empirical}D). But, critically, the drop in revenue in 2016 (20\%) is smaller than the drop in VDS effort (35\%). This supports a key prediction of our model: with trading, the relative revenue drop will be smaller than the relative effort drop but, without trading, the opposite relationship would hold (Fig. S4). At the PNA level, total revenues showed a net increase of \$64.7 and \$28 million USD for 2015 and 2016 respectively (Fig. S8), despite the PIPA closure.

@@

%%%% PLEASE TAKE A LOOK AT THE SECOND SENTENCE OF THIS PARAGRAPH %%%%
While trading would allow Palau, Kiribati, and other PNA members to reduce revenue losses from large-scale conservation, our model indicates that moving from a 40\% biomass-based allocation rule to a 100\% biomass-based rule would ensure long-term financial security in the presence of large-scale MPAs, and further incentivize conservation within the PNA. This is a model prediction that cannot be empirically tested in the PNA because the rule has not been experimentally modified. The PNA countries have shown that rights-based management of transboundary resources can result in large management and economic benefits \cite{havice_2013,aqorau_2018}. By facilitating trade and allocating rights based on biomass, they may also have become pioneers in effective large-scale marine conservation in a market-based setting.

There are, however, a series of important considerations to take into account. First, in our model only one of the countries considers the implementation of a protected area. An interesting extension could consider cooperative conservation. In that setting, a group of countries could coordinate on an optimized, large-scale strategic closure -perhaps using vessel-day trading as a means of compensation- in a manner similar to the model above. Future research could explore the role of heterogeneous costs and benefits between countries, and the way in which these can shape conservation outcomes in a market-based setting. A second consideration is the role of the high seas: environmental markets require secure property rights, which are lacking in the high seas \cite{crespo_2019}. Benefits accruing to the high seas could potentially be eroded by the prevailing open access conditions. Therefore, a conservation-minded nation has no mechanism to capture the benefits provided to the high seas, highligting the importance of empowering high seas governance and transboundary cooperation \cite{aqorau_2018,crespo_2019}. Finally, our work focuses on fisheries and large-scale conservation, but the framework could potentially be expanded and applied to other systems and natural resources. For example, similar mechanisms could be implemented in markets for tradable water rights \cite{rosegrant_1994} or game hunting \cite{hutton_2003} where secure property rights and the presence of a market may incentivise users to conserve the resource in question.

The use of environmental markets for conservation is a common but contentious approach among conservation scientists and resource managers \cite{sandbrook_2019}. One of the driving concerns is that markets may create incentives that lead to undesirable outcomes, thus emphasizing the need for careful design. We show that without cross country markets, individual countries have little incentive to undertake large-scale marine conservation, but that this incentive can be reversed if those countries are in an appropriately-designed market-based setting. For the market to create these incentives, certain design features are paramount. In the case of fishing rights and MPAs, cross-country transferable fishing rights and a biomass-based allocation rule are two necessary conditions to achieve the conservation incentive. International goals over the next decade have set ambitious targets for terrestrial and marine conservation, which will provide benefits ranging from preserving biodiversity to enhancing human well-being \cite{oleary_2016,dinerstein_2019,roberts_2017,ban_2019}. Our work shows how well-designed environmental markets can provide the right incentives for effective large-scale marine conservation.

@@

Country 1 considers a spatial closure by implementing a reserve as a fraction $R$ of the total country ($R \in[0,1)$). Fish move within a country based on $\theta$, where $\theta = 0$ implies no movement within the country, and $\theta = 1$ implies that fish move so much that they can be caught from anywhere within the country (see the \emph{Notes on within-country fish movement} section below). In this country, revenues are given by $pqE_1X_1(\theta R + (1 - R))$. The parenthetical term is the fishable fraction of biomass in Country 1. It assumes that fraction $\theta$ of fish inside the reserve at the beginning of the fishing season are fishable outside the reserve at some point during the course of the fishing season. The parameterization of movement and reserve size imply that profit from fishing Country 1 is given by:

@@

\noindent where $\Omega_1 = (\theta R + (1 - R))$. Also note that $\Omega_{i \neq 1} = 1$ since only Country 1 implements a reserve.

@@

\noindent The above equations imply that the marginal profit from the last unit of effort in a country is given by:

@@

In practice, the effort levels in each country are allocated by management (so $E_{1},\ E_{2},...,E_{9}$ are given) and the effort level on the high seas ($E_{10}$) is a result of open access dynamics. Therefore, we assume that effort continues to enter Country 10 until the profit from the last unit of effort is exactly zero, indicating that $E_{10}$ is the value for which $\pi_{10}(E_{10})  = 0$. Setting Equation \ref{eqn:marginal_profit} (for $i = 10$) equal to zero and removing $\Omega_{10} = 1$ for simplicity, we can solve for $E_{10}$:

@@

\begin{equation}
X_{t+1} = e_t \times  exp\left(r \left(1 - \frac{e_t}{K} \right)\right)
\label{eqn:grow}
\end{equation}

\noindent where $r$ and $K$ are species-specific intrinsic growth and carrying capacity parameters (the slope $\frac{dX_{t+1}}{de_t}|_{e_t=0}=exp(r)$). After the stock grows, a constant and country-specific fraction $f_i$ of the total stock redistributes to country $i$, so:

@@

In our model parameterization, the proportion of biomass ``available'' for harvest in the conserving country is given by  $\Omega_1 = (\theta R + (1 - R))$. This implies that for a given country with stock size $X_i$, the total biomass available for harvest will be given by $\Omega_i X_i$. Consider the case of a sesile fish with $\theta = 0$. If the country were to close 50\% of its waters to fishing ($R = 0.5$), only 50\% of the stock would be available for harvest (\emph{i.e.} $0 + (1 - 0) * (1 - 0.5) = 0.5$). Now, consider the same closure is applied with a stock with high mobility, so $\theta = 0.9$. In this case, despite the closure, fish frequently move between the reserve and fishing grounds making 95\% of biomass available for harvest (\emph{i.e.} $0.9 + (1 - 0.9) * (1 - 0.5) = 0.95$). As derived in the bioeconomic model above, a vessel's willingness to pay to fish in a given patch will be determined by the amount of biomass available for harvest. Within-patch stock movement therefore plays an important role in determining a vessel's willingness to pay in the remaining open waters: a vessel will be willing to pay more to fish in waters where 95\% of biomass is available for harvest, than when only 50\% of biomass is available for harvest.

@@

We run simulations under various market designs and test the model across a range of reserve sizes and within-country movement parameters.The first scenario does not allow trading. In this case, total allowable effort ($\bar{E}$) and biomass $B_{now}$ are known and equally distributed among Countries 1-9. For Country 10, we solve for Eq \ref{eqn:effort_hs} until biomass converges to match $B_{now}$. We then proceed to ``close'' a portion of Country 1, and calculate the vessel-day price in Country 1 given that only $X_i\Omega_i$ biomass is available for harvest. We compare vessel-day revenues of each scenario to a case with no reserve ($R = 0$). This produces a measure of the cost of implementing a spatial closure of size $R$ in Country 1.

The second scenario allows trading. We start again by solving for the high seas to obtain total effort. Since a closure is not in effect and VDS-managed effort is equally distributed across the 9 countries, this equilibrium is the same as the first step above. We then implement a spatial closure in Country 1. This essentially lowers the price fishers would be willing to pay to fish in a country with only biomass $X_i\Omega_i$, lowering demand for vessel-days in Country 1. Countries 2 - 9 have a higher demand for vessel days, and therefore a portion of vessel-days from Country 1 are sold to Countries 2 - 9. This increases effort in these countries, which reduces escapement and therefore biomass. This reduction in biomass in turn will modify the marginal profit and willingness to pay to fish in each country. We iterate this process until biomass stabilizes. Like before, we calculate vessel-day revenues to each country and compare them to a case with no reserve in Country 1.

Annual vessel-days are often allocated based on a combination of historical within-country effort and biomass. In the PNA, 60\% of the allocation is calculated based on EEZ effort over the last seven years and 40\% is calculated based on the 10-year average of each country’s share of estimated biomass (of skipjack and yellowfin tuna) within its EEZ (see Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}). Trading vessel-days to other countries would imply that historical within-country effort declines through time. The allocated days to a country with a full spatial closure would eventually be reduced to just the 40\% based on biomass.

In the trading scenario above, effort from Country 1 (with the reserve) is traded to other countries. This means that its allocation will decrease as purse seine effort in Country 1 is reduced. To analyze the consequences of different allocation rules when trading is allowed, we simulate a fishery 50 years into the future, and annually re-allocate vessel-days based on a 7-year running mean of country-level effort and biomass. At the end of every time period (a year), vessel-days are re-allocated to each country based on the following rule:

@@

We can then compare the location of displaced and non-displaced vessels before and after the implementation of PIPA to better understand the effort redistribution. Non-displaced vessels serve as a plausible control group that was not subject to a spatial closure but might have redistributed in response to changing environmental conditions, such as El Ni\~no \cite{hanich2018unraveling,aqorau_2018}.

@@

Juan Carlos Villaseñor-Derbez was supported by UCMexus-CONACyT (CVU: 669403) and the Latin American Fisheries Fellowship Program. John Lynham was supported by the Conservation Strategy Fund, with a grant from the Pew Charitable Trusts and Pew Bertarelli Ocean Legacy. John Lynham and Christopher Costello wish to acknowledge The Nature Conservancy. We thank Rachel Dacks for valuable research assistance.

@@

% Costs of different allocation rules
\begin{figure}[htbp]
\centering
\includegraphics{img/allocation_cost_plot.pdf}
\caption{\label{fig:allocation_cost_plot}Costs of a spatial closure for Country 1 under different allocation rules. Each line represents the revenue losses for a combination of allocation rules ($\alpha$; line type) and movement ($\theta$; color) for different reserve sizes ($R$; horizontal axis). A value of $\alpha = 1$ implies that allocations are based entirely on historical effort, while a value of $\alpha = 0$ implies a 100\% biomass-based allocation rule. A value of $\theta = 0$ represents a stock that doesn't move, and $\theta = 1$ depics a stock that continuously moves between the reserve and the fishing zone. The proportion of the Exclusive Economic Zone closed to fishing is given by $R$. An effort-based allocation and low within-country movement values result in the highest costs. Cost can be minimized for all movement values if allocation is based on biomass within each country's waters.}
\end{figure}

### 2019-10-25 docs/Supplementary_materials.tex
Updated docs folder

\begin{table}[H]
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{l|r|l}
\hline
Parameter & Value & Source\\
\hline
MSY & 1.875600e+06 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
\hline
$B_{msy}$ & 1.628000e+06 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
\hline
K & 6.876526e+06 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
\hline
$B_c/B_{msy}$ & 0.51 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
\hline
$C_{now}$ & 1.679444e+06 & Catches from WCPFC Stock Assessment\\
\hline
$B_{now}$ & 3.507028e+06 & Current Biomass (2012 - 2015 average)\\
\hline
$r$ & 0.57 & From FishBase: Prior r = 0.57, 95 CL = 0.41 - 0.78\\
\hline
$\beta$ & 1.3 & Standard \cite{costello_2016}\\
\hline
p & 1100 & Mean between Thailand and Japan values (Value of WCPFC-CA Tuna Fisheries 2017 Report)\\
\hline
q & 3.420000e-05 & Estimated so that efforts match catches given biomass and vessel-day prices\\
\hline
c & 1800 & Estimated to match cost and revenue structures\\
\hline
f & 0.1 & Biomass is equally distributed between countries\\
\hline
\end{tabular}}
\end{table}

@@

We observe four characteristics for every vessel: crew size, engine power, vessel length, and tonnage capacity. Figure \ref{fig:balance_density_plot} shows the distribution of these variables for each group of vessels. Table \ref{tab:balance_table} presentsibut the mean, and standard deviation of each observable. Group of vessels are similar on observables, and choice to fish inside PIPA before implementation does not appear to be driven by observable characteristics.

@@

\caption{\label{tab:balance_table}Mean values on observable characteristics by vessel for displaced (n = 64), and non-displaced vessels (n = 254). Numbers in parentheses indicate standard deviation. The last column contains the difference in means (t-scores), with asterisks inicating significant differences as indicated by a two-tailed t-test (* p $<$ 0.1; ** p $<$ 0.05; *** p $<$ 0.01).}
\centering
\begin{tabular}{l|l|l|l}
\hline
Characteristic & Displaced & Non-displaced & Difference\\
\hline
Crew size (n) & 26.38 (3.94) & 30.46 (6.25) & 4.08 (6.49) ***\\
\hline
Engine Power (KW) & 2983.6 (558.76) & 2559.89 (588.28) & -423.71 (-5.36) ***\\
\hline
Length (m) & 74.23 (9.71) & 68.97 (8.42) & -5.25 (-3.97) ***\\
\hline
Tonnage (GT) & 1718.14 (653.38) & 1383.41 (533.56) & -334.73 (-3.79) ***\\
\hline
\end{tabular}
\end{table}

>>>>

	\caption{\label{tab:param_table}Model parameters.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{l|r|l}
\hline
Parameter & Value & Source\\
\hline
MSY & 1.875600e+06 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
\hline
$B_{msy}$ & 1.628000e+06 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
\hline
K & 6.876526e+06 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
\hline
$B_c/B_{msy}$ & 0.51 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
\hline
$C_{now}$ & 1.679444e+06 & Catches from WCPFC Stock Assessment\\
\hline
$B_{now}$ & 3.507028e+06 & Current Biomass (2012 - 2015 average)\\
\hline
$r$ & 0.57 & From FishBase: Prior r = 0.57, 95 CL = 0.41 - 0.78\\
\hline
$\beta$ & 1.3 & Standard \cite{costello_2016}\\
\hline
p & 1100 & Mean between Thailand and Japan values (Value of WCPFC-CA Tuna Fisheries 2017 Report)\\
\hline
q & 3.420000e-05 & Estimated so that efforts match catches given biomass and vessel-day prices\\
\hline
c & 1800 & Estimated to match cost and revenue structures\\
\hline
f & 0.1 & Biomass is equally distributed between countries\\
\hline
\end{tabular}}
\end{table}

@@

We observe four characteristics for every vessel: crew size, engine power, vessel length, and tonnage capacity. Figure \ref{fig:balance_density_plot} shows the distribution of these variables for each group of vessels. Table \ref{tab:balance_table} presents the mean and standard deviation of each observable. On average, displaced vessels have smaller crew sizes, more engine power, and are larger than non-displaced vessels. The largest relative difference is in terms of gross tonnage.

@@

\caption{\label{tab:balance_table}Mean values on observable characteristics by vessel for displaced (n = 64), and non-displaced vessels (n = 254). Numbers in parentheses indicate standard deviation. The last column contains the difference in means (t-scores), with asterisks indicating significant differences as indicated by a two-tailed t-test (* p $<$ 0.1; ** p $<$ 0.05; *** p $<$ 0.01).}
\centering
\begin{tabular}{l|l|l|l}
\hline
Characteristic & Displaced & Non-displaced & Difference\\
\hline
Crew size (n) & 26.38 (3.94) & 30.46 (6.25) & 4.08 (6.49) ***\\
\hline
Engine Power (KW) & 2983.6 (558.76) & 2559.89 (588.28) & -423.71 (-5.36) ***\\
\hline
Length (m) & 74.23 (9.71) & 68.97 (8.42) & -5.25 (-3.97) ***\\
\hline
Tonnage (GT) & 1718.14 (653.38) & 1383.41 (533.56) & -334.73 (-3.79) ***\\
\hline
\end{tabular}
\end{table}
